---
title: "Chargeback Fraud Prediction R Notebook"
output: html_notebook
---

```{r}
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```


```{r}
#getwd()
#list.files()
cbf <- read.csv("df.csv")
```
```{r}
# libraries
library(caret)
library(tidyverse)
library(tidymodels)
library(skimr)
library(knitr)
```


```{r}
cbf %>% skim()
```

This is a case for Univariate Time Series CLASSIFICATION.
 
```{r}
cbf_ts <- cbf[c("Date", "Amount", "CBK")]
head(cbf_ts)
```
 
```{r}
cbf_ts$Date <- as.POSIXct(cbf_ts$Date, format="%Y-%m-%d %H:%M:%S")
```

```{r, out.width= 14}
library(lubridate)
table(year(cbf_ts$Date), month(cbf_ts$Date))
table(month(cbf_ts$Date), day(cbf_ts$Date))
table(day(cbf_ts$Date), hour(cbf_ts$Date))
#table(hour(cbf_ts$Date))
```

From the above results we can see that all this data is collected in 2015, in the Month of MAY(5), for 30 DAYS.
Also it appears that 9 AM till 12 AM is the most ACTIVE time for Shopping.


```{r}
# Let's check if there is a pattern by the Hour, for committing Fraud Transactions
ggplot(cbf_ts, aes(x = hour(Date), y = Amount, colour = cbf_ts$CBK)) + geom_point()
```

All FRAUD Transactions have a monetary value of <= 1000 and there appears NO pattern by the Hour for committing FRAUD transactions.

Also, MOST High value transactions are happening between 10 AM & 8 PM.

```{r}
# Let's check for pattern by Date
ggplot(cbf_ts, aes(x = day(Date), y = Amount, colour = cbf_ts$CBK)) + geom_point()
```

All FRAUD Transactions have a monetary value of <= 1000 and there appears NO pattern by the Day for committing FRAUD transactions.

Also, MOST High value transactions are happening between 25th & 28th days of the Month.

```{r}
library(plotly)
```

{fig.height = 3, fig.width = 3, fig.align = "center"}

```{r}
# Let's look at the Most active time of the day for transactions

p <- ggplot(data=cbf_ts, aes(day(cbf_ts$Date), colour = cbf_ts$CBK, fill = cbf_ts$CBK)) + 
  geom_histogram(col = 100, bins = 35) +
  labs(title="Histogram for No. of Transactions by Date") +
  labs(x="DATE", y="Count") + 
  xlim(c(1,31))
p <- p + labs(fill = "FRAUD TRANSACTION") 
ggplotly(p)
```

```{r}
ggplot(data = cbf_ts, aes(x = day(cbf_ts$Date), y = Amount, group = CBK, colour = CBK)) +
    geom_smooth(fullrange = TRUE) +
    labs(title="TREND of FRADULENT TRANSACTIONS by DATE ") +
    labs(x="DATE", y="AMOUNT")
```

Most High Valued Fradulent transactions appear to be happening, in the Beginning of the month, and the Value of Fradulent Transactions is tapering down as it reaches Monthend

```{r}
ggplot(data = cbf_ts, aes(x = hour(cbf_ts$Date), y = Amount, group = CBK, colour = CBK)) +
    geom_smooth(fullrange = TRUE) +
    labs(title="TREND of FRADULENT TRANSACTIONS by HOUR ") +
    labs(x="HOUR", y="AMOUNT")
```


The Value of Fradulent transactions appear to be increasing, as the Day progresses to Midnight starting from Afternoon around 3 o Clock.

```{r, fig.width=14, fig.height=8}
plot(table(hour(cbf_ts$Date), day(cbf_ts$Date)), col = cbf_ts$Amount, main = "Transaction by Hour & Date")

```


```{r}
library(ggplot2)
```


```{r}
p <- ggplot(cbf_ts, aes(day(cbf_ts$Date)))
p + geom_bar(aes(fill = hour(cbf_ts$Date))) +
scale_x_continuous(breaks = scales::pretty_breaks(n = 31)) 
#scale_y_continuous(breaks = scales::pretty_breaks(n = 31))

```


```{r, fig.width=20, fig.height=20}
p = ggplot(tbl, aes(Date, Freq, fill = Hour)) + geom_bar(stat="identity")

p + geom_text(aes(label = Freq), size = 3, hjust = 0.5, vjust = 3, position =     "stack") 
```

```{r, fig.width=20, fig.height=20}
p3 <- ggplot(tbl[order(tbl$Hour,decreasing=TRUE),], aes(Date, Freq, fill = Hour))+
  geom_bar(stat="identity") + labs(title="No. of Transactions within the Hour by DAY")

p3 <- p3 + geom_text(aes(label = Freq), size = 5, hjust = 0.5, vjust = 3, position = "stack") 

ggplotly(p3)

```

